A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-08-29 ionic_liquids.tex

\usepackage[T1]{fontenc}

@@

In the following, the subscripts ``$s$'' and ``$\text{IL}$'' refer to the solute and the solvent (ionic liquid), respectively.
For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
\begin{equation}
\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 0)}, 
\end{equation}
where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy.
They found out that
\begin{equation}
\begin{split}
\label{eq:free_solv}
 \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
\end{split}
\end{equation}
where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid phase and $P_s$ is the partial pressure of the solute in the gas phase.
It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.

@@

Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which was derived by refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
This refining was characterized by their authors as ``unusual'', given that the LJ parameters were modified, while keeping the partial charges at their original values.
This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry constants of \ce{CO_2} at several temperatures.

@@

As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ yield more decorrelated samples in each subensemble.
In this work, we employ $N^{EE}$ = 5 which, together with the specified $\lambda_{\, \text{vdW}}$ set, resulted to be satisfactory as up to 3 preliminary runs of the EE were enough to determine the weights $\eta$ that yielded, in a final simulation, a ``sufficient'' sampling of each subensamble.
By ``sufficient'', we mean that the sampling provides an acceptable uncertainty in $\Delta G$.
The simulation times for the preliminary and final EE runs were 10 and 40 ns, respectively; and each $\lambda_{\text{Coul}}$ state was simulated for 10 ns.
Finally, the MBAR method \cite{Shirts_2008}, as implemented by Klimovich \textit{et al.} \cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$.

@@

A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
The CDF of the dihedrals angles of C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the results of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 is 0$^{\circ}$.
This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.} \cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy for building the rigid bodies is required.
Thus, the simulations of \ce{[emim][NTf_2]} were performed considering flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.

@@

\begin{table*}
\begin{threeparttable}
\caption{Comparison of predicted and experimental densities for differents models of \ce{[emim][B(CN)_4]} via NPT-MD simulations at $T = 298.0~\text{K}$ and $P = 1.0~\text{atm}$. The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
\begin{tabular}{ c  c  c  c  c}  
\hline \hline
$\text{[emim]}$[B(CN)\textsubscript{4}] &  $\rho_{\text{sim}}$ & error (\%)\tnote{a}  & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
model & (g/cm$^{3}$) &  &  (g/cm$^{3}$) &  \\
			\hline
& \multicolumn{2}{c}{Flexible ions/Ewald method} & \multicolumn{2}{c}{Rigid ions/DSF method} \\
Koller y col. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
Batista y col. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
Liu y col. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
Weber y Kirchner. \cite{Weber_2016} & 1.015 & 2.1 & 1.022 & 1.4  \\
 \hline \hline
\label{table:props_dsf} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^{\text{sim}}$)/$\rho^{\text{exp}}$.
\end{tablenotes}
\end{threeparttable}
\end{table*}

@@

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at $T$ = $298.15~\text{K}$ and $P$ = $1~\text{atm}$.
The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
\begin{tabular}{ c c c  c  c  c  c }  
\toprule
Model & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
			\hline
			\multicolumn{4}{c}{\ce{[emim][B(CN)_4]}} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
			\hline
Koller \textit{et al.} \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
Batista \textit{et al.} \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
Liu \textit{et al.} \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
\hline
		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
		\hline
 K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
 \bottomrule
\label{table:henry} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

It should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
Moreover, the $\Delta G_{\text{sim}}$ in [emim][Tf\textsubscript{2}N] is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
These consistencies have served for validating the methodological approaches of this work.

@@

The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf\textsubscript{2}]}. 
The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm this result.
The SDFs of the ions around a \ce{CO_2} molecule were obtained by using the software packages TRAVIS \cite{Brehm_2011} and VMD \cite{HUMP96}.
For that, we carried out NPT-MD simulations of \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] systems with a \ce{CO_2} molar fraction of 0.1.
The isovalues were visually determined so as to observe the first solvation shell.
If we compare Figs.~\ref{fig:sdf_ions} (a) and (b), one notes that the region with a low probability of finding an ion is larger for \ce{[emim][NTf_2]}.
Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.~\ref{fig:sdf_ions} (c).
\begin{figure}[ht]
\centering
\subfloat[]{%
  \includegraphics[width=\linewidth]{kollerall.pdf}%
}

@@

\subsection{Study of concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]}
\label{sec:results_conc}

Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table~\ref{table:solv}, which correspond to similar values of \ce{CO_2} molality.
Note that the differences in the \ce{CO_2} molar fractions clearly exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, which was mentioned at the introduction of this paper.

\begin{table*}
\centering
\begin{threeparttable}
\caption{Thermodynamic conditions employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}~\cite{Makino_2014,Schilderman_2007}.}
\begin{tabular}{ c  c  c  c  c  }  
\toprule
Ionic liquid & T (K)  & P (atm)  & molar fraction $x_s$ & molality $m_s$ \\
\midrule		
$\text{[emim]}$[B(CN)\textsubscript{4}]~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
$\text{[emim]}$[Tf\textsubscript{2}N]~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
 \bottomrule
\label{table:solv} 
\end{tabular}
\end{threeparttable}
\end{table*}

For each system, in Fig.~\ref{fig:pressure} we show our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably lower for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
In addition, we see that in this case the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively.
However, since we simulated a different molecule number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could be a factor contributing to the higher solubility.

@@

We focused also on exploring alternative simulation strategies with the goal of gaining computational efficiency.
Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, we concluded that the DSF method with $\alpha$ = 0.2 {\AA}$^{-1}$ is a suitable strategy.
Other improvement was the use of rigid bodies to simulate \ce{[emim][B(CN)_4]}.
This required preliminary simulations in order to examine the flexibility of the ethyl chain in \ce{[emim]^+} and the analysis was greatly facilitated by employing useful visualization tools.
It should be remarked that the different models presented a different behavior, as well; reflecting ?

The solvation free energy results at infinite-dilution condition suggest a slightly more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in  \ce{[emim][NTf_2]}.
However, this picture completely changes at high concentrations: the simulations correctly predicted a considerable lower pressure to dissolve a certain mass of \ce{CO_2} in \ce{[emim][B(CN)_4]}.

Finally, we employed the model of Koller \textit{et al.} \cite{Koller_2012} to predict infinite-dilution activity coefficient of various solutes.
In this case, the results were not satisfactory given the high errors associated to the free energy calculations of the pure solutes, making necessary a revision of the force fields for the solutes in a future work.

>>>>

\usepackage[T1]{fontenc}
\usepackage{xr}
\externaldocument{supp_material}

@@

In the following, the subscripts ``$s$'' and ``$\text{IL}$'' refer to the solute and the solvent (ionic liquid), respectively.
For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
\begin{equation}
\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 0)}, 
\end{equation}
where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy.
They found out that
\begin{equation}
\begin{split}
\label{eq:free_solv}
 \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
\end{split}
\end{equation}
where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid-phase and $P_s$ is the partial pressure of the solute in the gas phase.
It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.

@@

Finally, for \ce{[emim][NTf_2]} we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which was derived by refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
This refining was characterized by their authors as ``unusual'', given that the LJ parameters were modified, while keeping the partial charges at their original values.
This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry constants of \ce{CO_2} at several temperatures.

@@

As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ yield more decorrelated samples in each subensemble.
In this work, we employed $N^{EE}$ = 5 which, together with the specified $\lambda_{\, \text{vdW}}$ set, required up to 3 preliminary runs of the EE for determining the weights $\eta$ that yielded, in a final simulation, a ``sufficient'' sampling of each subensamble.
By ``sufficient'', we mean that the sampling provides an acceptable uncertainty in $\Delta G$.
The simulation times for the preliminary and final EE runs were 10 and 40 ns, respectively; and each $\lambda_{\text{Coul}}$ state was simulated for 10 ns.
Finally, the MBAR method \cite{Shirts_2008}, as implemented by Klimovich \textit{et al.} \cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$.

@@

A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
The CDF of the dihedrals angles of C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the results of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 is 0$^{\circ}$.
This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.} \cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy for building the rigid bodies is required.
Thus, the simulations of \ce{[emim][NTf_2]} were performed considering flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.

@@

\begin{table*}
\begin{threeparttable}
\caption{Comparison of predicted and experimental densities for differents models of \ce{[emim][B(CN)_4]} via NPT-MD simulations at $T = 298.0~\text{K}$ and $P = 1.0~\text{atm}$. The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
\begin{tabular}{ c  c  c  c  c}  
\hline \hline
\ce{[emim][B(CN)_4]}&  $\rho_{\text{sim}}$ & error (\%)\tnote{a}  & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
model & (g/cm$^{3}$) &  &  (g/cm$^{3}$) &  \\
			\hline
& \multicolumn{2}{c}{Flexible ions/Ewald method} & \multicolumn{2}{c}{Rigid ions/DSF method} \\
Koller y col. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
Batista y col. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
Liu y col. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
Weber y Kirchner. \cite{Weber_2016} & 1.015 & 2.1 & 1.022 & 1.4  \\
 \hline \hline
\label{table:props_dsf} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^{\text{sim}}$)/$\rho^{\text{exp}}$.
\end{tablenotes}
\end{threeparttable}
\end{table*}

@@

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} at $T$ = $298.15~\text{K}$ and $P$ = $1~\text{atm}$.
The experimental Henry constants in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
\begin{tabular}{ c c c  c  c  c  c }  
\toprule
Model & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
			\hline
			\multicolumn{4}{c}{\ce{[emim][B(CN)_4]}} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
			\hline
Koller \textit{et al.} \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
Batista \textit{et al.} \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
Liu \textit{et al.} \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
\hline
		\multicolumn{4}{c}{\ce{[emim][NTf_2]}} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
		\hline
 K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
 \bottomrule
\label{table:henry} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

It should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
Moreover, the $\Delta G_{\text{sim}}$ in \ce{[emim][NTf_2]} is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
These consistencies have served for validating the methodological approaches of this work.

@@

The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}. 
The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm this result.
The SDFs of the ions around a \ce{CO_2} molecule were obtained by using the software packages TRAVIS \cite{Brehm_2011} and VMD \cite{HUMP96}.
For that, we carried out NPT-MD simulations of \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} systems with a \ce{CO_2} molar fraction of 0.1.
The isovalues were visually determined so as to observe the first solvation shell.
If we compare Figs.~\ref{fig:sdf_ions} (a) and (b), one notes that the region with a low probability of finding an ion is larger for \ce{[emim][NTf_2]}.
Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.~\ref{fig:sdf_ions} (c).
\begin{figure}[ht]
\centering
\subfloat[]{%
  \includegraphics[width=\linewidth]{kollerall.pdf}%
}

@@

\subsection{Study of concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
\label{sec:results_conc}

Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we have also carried out simulations at the thermodynamic conditions specified in Table~\ref{table:solv}, which correspond to similar values of \ce{CO_2} molality.
Note that the differences in the \ce{CO_2} molar fractions clearly exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.

\begin{table*}
\centering
\begin{threeparttable}
\caption{Thermodynamic conditions employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}~\cite{Makino_2014,Schilderman_2007}.}
\begin{tabular}{ c  c  c  c  c  }  
\toprule
Ionic liquid & T (K)  & P (atm)  & molar fraction $x_s$ & molality $m_s$ \\
\midrule		
\ce{[emim][B(CN)_4]}~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
\ce{[emim][NTf_2]}~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
 \bottomrule
\label{table:solv} 
\end{tabular}
\end{threeparttable}
\end{table*}

For each system, in Fig.~\ref{fig:pressure} we show our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably lower for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
In addition, we see that in this case the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively.
However, since we simulated a different number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could explain the higher solubility.

@@

We focused also on exploring alternative simulation strategies with the goal of gaining computational efficiency.
Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, we concluded that the DSF method with $\alpha$ = 0.2 {\AA}$^{-1}$ is a suitable strategy.
Other improvement was the use of rigid bodies to simulate \ce{[emim][B(CN)_4]}.
This required preliminary simulations in order to examine the flexibility of the ethyl chain in \ce{[emim]^+} and the analysis was greatly facilitated by employing useful visualization tools.
Besides the properties already mentioned, the different models showed quite different behaviors, as well.
This lack of consistency is one of the reasons why in industry molecular simulation has not become a routinely tool yet.

The solvation free energy results at infinite-dilution condition suggest a slightly more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in  \ce{[emim][NTf_2]}.
However, this picture changes at high concentrations: the simulations correctly predicted a considerable lower pressure to dissolve a certain mass of \ce{CO_2} in \ce{[emim][B(CN)_4]}.

Finally, we employed the model of Koller \textit{et al.} \cite{Koller_2012} to predict infinite-dilution activity coefficients of various solutes.
In this case, the results were not satisfactory given the large errors in the free energy calculations of the pure solutes, making necessary a revision of their force fields in a future work.
